Revisiting the zonally asymmetric extratropical circulation of the Southern Hemisphere spring using complex empirical orthogonal functions

### 2023-04-23 analysis/paper/shceof.Rmd
Adds support for HTML version

output: 
  # bookdown::word_document2:
  #     pandoc_args: ["--lua-filter=abstract-to-meta.lua", "--wrap=preserve"]
  bookdown::pdf_document2:
      latex_engine: "xelatex"
      keep_tex: true
      citation_package: "natbib"
      template: "template.tex"
      pandoc_args: ["--lua-filter=abstract-to-meta.lua", "--wrap=preserve"]
always_allow_html: true
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 # - \usepackage{natbib}
 # - \usepackage{lineno}
 # - \linenumbers 
---

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 41,
  cache.path = "../cache/paper/",
  # fig.path = "../figures/",
  dpi = 300,
  dev = c("pdf", "png")
)

>>>>

output: 
  bookdown::html_document2:
      code_folding: "hide"
  # bookdown::word_document2:
  #     pandoc_args: ["--lua-filter=abstract-to-meta.lua", "--wrap=preserve"]
  bookdown::pdf_document2:
      latex_engine: "xelatex"
      keep_tex: true
      citation_package: "natbib"
      template: "template.tex"
      pandoc_args: ["--lua-filter=abstract-to-meta.lua", "--wrap=preserve"]
always_allow_html: true
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 # - \usepackage{natbib}
 # - \usepackage{lineno}
 # - \linenumbers 
---

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 41,
  cache.path = "../cache/paper/",
  # fig.path = "../figures/",
  dpi = 300,
  dev = if (knitr::is_html_output()) c("png") else c("pdf", "png")
)
